### 2021-11-24 thesis/tex/ICintro.tex
update
added muon decays

\section{Neutrino detection}
%TODO: Write down detection process. This section should be written carefully. 
% Specify the guys going into NC and CC. 
% First line only true for CC
% In next lines ,detail the detection process (interaction with detector matter osv). 
% Specify which are occurring in tracks and cascades.
We always observe neutrinos indirectly through their associated charged lepton. 
Regardless of the type of interaction (charged current via the $W$ boson, or neutral current
via the $Z$), a charged lepton exits with altered properties. The lepton is then detected, and the properties of the neutrino involved in the 
interaction are then deduced. This deduction will be imperfect, and this introduces complexities that we will handle in Ch.~\ref{ch:ICmethod}.

In this work, we only study the detectors handled by the IceCube collaboration. They are of Cherenkov type, which means that they detect 
the secondary charged lepton by its emitted Cherenkov light, produced from its travel through the Antarctic ice. 
To detect the Cherenkov light, 60 Digital Optical Modules (DOMs) are placed on a long string up to \SI{17}{\metre} apart. 86 of these strings are then lowered
into \SI{2.5}{\km} deep boreholes in the ice. The holes are then sealed by refreezing the ice, resulting in a total of 5160 DOMs in a volume of approximately \SI{1}{\km^3}~\cite{weaverThesis}.

@@

If the charged leptons interact heavily with the ice, they will travel a short distance and emit a localized flash of 
Cherenkov light. This event is referred to as a cascade. The neutral current interactions involve quarks, which recoils and produces
showers of hadrons. Also, charged current $\ne$ interactions also produce cascades. A cascade event 
is shown in Fig.~\ref{fig:events_cascade}.
% S wanted to remove below. Why?
If the charged leptons don't interact as much in the ice, they penetrate a larger part of it, emitting light and tertiary particles
as they go. This event is referred to as a track and is often due to charged current muon interactions. A track event 
is shown in Fig.~\ref{fig:events_track}. 
%TODO: numbers on how often^. Write about which particles appear where

@@

\subsection{Atmospheric Neutrino Flux}
Atmospheric neutrinos originate from cosmic rays composed of high-energy protons interacting with nuclei in the atmosphere.
These interactions ultimately produces pions, which decay as 
\begin{align}\label{eq:pion} %Incorrect. Add muon decays
    &\pi^+ \to \mu^+ + \nm\,, \quad \pi^- \to \mu^- + \anm \nonumber \\
    &\pi^+ \to e^+ + \ne\,,\,\, \quad \pi^- \to e^- + \ane\,.
\end{align}
In the muonic decay channel, muons are emitted which will be detected by the IceCube detector.

@@

\begin{figure}[t]
    \centering
    %TODO: rework
    \includegraphics[width=0.9\textwidth]{figures/flux.pdf}
    \caption{Interpolated South Pole atmospheric $\nu_\mu$ flux with data from~\cite{hondaArticle}, displaying a weak 
    zenith angle dependance, but a strong energy dependence. The energy dependence can be parametrized to be approximated by $E^{-2.7}$.}\label{fig:flux}
\end{figure}

>>>>

\section{Neutrino detection}
%TODO: Write down detection process. This section should be written carefully. 
% Specify the guys going into NC and CC. 
% First line only true for CC
% In next lines ,detail the detection process (interaction with detector matter osv). 
% Specify which are occurring in tracks and cascades.
We always observe neutrinos indirectly.
Regardless of the type of interaction (charged current via the $W$ boson, or neutral current
via the $Z$), a fermion (which is not another neutrino) exits with altered properties. This fermion is then directly or indirectly detected, 
and the properties of the neutrino involved in the 
interaction are then deduced. This deduction will be imperfect, and this introduces complexities that we will handle in Ch.~\ref{ch:ICmethod}.

In this work, we only study the detectors buried within the Antarctic ice by the IceCube collaboration. 
They are of Cherenkov type, which means that they detect 
a charged lepton by its emitted Cherenkov light, produced from its travel through the ice. 
In the case of CC interactions, this charged lepton is directly involved in the interaction with the neutrino, either as 
both incoming and outgoing particles, or as only the outgoing particle in the case of a hadronic CC interaction.
In the case of NC interactions, the flavor of the fermion interacting with the neutrino is unchanged, but energy 
from the neutrino will be transferred to the fermion that violently recoils, later producing a shower of tertiary particles.

If the secondary particles interact heavily with the ice, they will only travel a short distance before decaying 
into the shower which emit a localized flash of Cherenkov light. This event is referred to as a cascade.
NC interactions tend to be classified as cascades due to the production of a localized hadronic shower
However, CC $\ne$ interactions can also produce a similar localized flash of Cherenkov light, causing them to also contribute 
to the cascade events. A cascade event 
is shown in Fig.~\ref{fig:events_cascade}.

If the charged leptons don't interact as much in the ice, they penetrate a larger part of it, emitting light and tertiary particles
as they go. This event is referred to as a track and is often due to charged current muon interactions. A track event 
is shown in Fig.~\ref{fig:events_track}.

So NC interactions and CC $\ne$ interactions are usually classified as cascades, while CC $\nm$ interactions are usually tagged 
as a track. So what about CC $\nt$? Due to the heaviness of the $\tau$, it rapidly decays - primarily into hadrons - giving us a short path
of travel with a final shower, thus manifesting themselves as a cascade~\cite{DC2019tauappearance}. We summarize the above classification 
information in Table~\ref{table:events}, containting classifications from `Sample B' of a 2019 DeepCore study~\cite{DC2019tauappearance}.

\begin{table}[h]
    \begin{center}
        \begin{tabular}{lcccccc}
            \hline \hline
            Interaction &Track &Cascade\\
            \hline
            CC $\ne$ & 30\%& 70\% \\
            CC $\nm$ & 70\%&30\% \\
            CC $\nt$ & 29\%& 71\%\\
            NC $\nu$ & 24\%& 76\%\\
            \hline \hline
        \end{tabular}
    \end{center}
    \caption{The neutrino event classification at \SI{56}{\GeV} from `Sample B' in~\cite{DC2019tauappearance}}\label{table:events}
\end{table}

To detect the Cherenkov light, 60 Digital Optical Modules (DOMs) are placed on a long string up to \SI{17}{\metre} apart. 86 of these strings are then lowered
into \SI{2.5}{\km} deep boreholes in the ice. The holes are then sealed by refreezing the ice, resulting in a total of 5160 DOMs in a volume of approximately \SI{1}{\km^3}~\cite{weaverThesis}.

@@

@@

\subsection{Atmospheric Neutrino Flux}
Atmospheric neutrinos originate from cosmic rays composed of high-energy protons interacting with nuclei in the atmosphere.
These interactions ultimately produces pions, which decay as 
\begin{align}\label{eq:pion}
    &\pi^+ \to \mu^+ + \nm\,, \quad \pi^- \to \mu^- + \anm \nonumber \\
    &\pi^+ \to e^+ + \ne\,,\,\, \quad \pi^- \to e^- + \ane\,.
\end{align}
The heavy muon ($m_\mu \approx 200m_e$) decays further:
\begin{align}
    &\mu^+ \to e^+ + \ne + \anm\,, \quad \mu^- \to e^- + \ane + \nm\,,
\end{align}
producing even more neutrinos.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=0.9\textwidth]{figures/flux.pdf}
    \caption{Interpolated South Pole atmospheric $\nu_\mu$ flux with data from~\cite{hondaArticle}, displaying a weak 
    zenith angle dependance, but a strong energy dependence. The energy dependence can be parametrized to be approximated by $E^{-2.7}$.}\label{fig:flux}
\end{figure}

### 2021-11-24 thesis/tex/ICtheory.tex
update

We deemed these shapes to be satisfactory, thus allowing us to multiply Eq.~\ref{eq:ICevents} by the 
correction factors of Eq.~\ref{eq:MC_norm}. We now arrive to our final event count
\begin{align}\label{eq:Nth}
    N_{ij} &= \frac{N_{ij}^\text{null}}{N_{ij}^\text{MC}} T \sum_\beta \int_{(\cos{\theta_z^r})_i}^{(\cos{\theta_z^r})_{i+1}} \dd \cos{\theta^r_z} \int_{E^r_{j}}^{E^r_{j+1}} \dd E^r 
    \int_{E^t_{min}}^{E^t_{max}} R(E^r,E^t) \phi_\beta^\text{det}  A^\text{eff}_\beta\, \dd E^t
    \,,
\end{align}
with $E^t_{min}$, $E^t_{max}$, and $R(E^r,E^t)$ taken from the Gaussian process regressor.
\begin{figure}[ht]
    \begin{centering}
    \includegraphics[scale=0.8]{figures/IC_MC_norm.pdf}
    \caption{IceCube Monte Carlo, binned in $\Ereco$ and $\zreco$. We compare this with our simulations shown as `Null' in the plots.}\label{fig:IC_MC_norm}
    \end{centering}
\end{figure} 
Thus, we are now able to sufficiently approximate the IceCube Monte Carlo, which makes us able to run simulations based on different physics scenarios.
% \newpage
% \bibliographystyle{nature}
% \bibliography{ref.bib}
% \end{document}

>>>>

We deemed these shapes to be satisfactory, thus allowing us to multiply Eq.~\ref{eq:ICevents} by the 
correction factors of Eq.~\ref{eq:MC_norm}.
\begin{figure}[ht]
    \begin{centering}
    \includegraphics[scale=0.8]{figures/IC_MC_norm.pdf}
    \caption{IceCube Monte Carlo, binned in $\Ereco$ and $\zreco$. We compare this with our simulations shown as `Null' in the plots.}\label{fig:IC_MC_norm}
    \end{centering}
\end{figure} 
Thus, we are now able to sufficiently approximate the IceCube Monte Carlo, which makes us able to run simulations based on different physics scenarios.
% \newpage
% \bibliographystyle{nature}
% \bibliography{ref.bib}
% \end{document}
